% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Yash Govind}

\basicInfo{
  ygovind@cs.wisc.edu \textperiodcentered\
  (+1)703-798-5998 \textperiodcentered\
  linkedin.com/in/ygovind \textperiodcentered\
  cs.wisc.edu/\textasciitilde{}ygovind/}

\section{Research Interests}
Data Management, Data Integration, Entity Matching, Machine Learning, Crowdsourcing.

\section{Education}
\datedsubsection{\textbf{University of Wisconsin - Madison}, WI, USA}{Fall 2014 -- present}
\textit{Ph.D. Computer Sciences} GPA: 3.85 / 4.0 {Advisor: Prof. AnHai Doan}
\begin{itemize}
\item Cloudmatcher: Building a hands-off cloud/crowd service for entity matching.
\end{itemize}
\datedsubsection{\textbf{Pt. Ravi Shankar Shukla University}, India}{Fall 2003 -- Spring 2007}
\textit{B.E.} in Computer Science and Engineering GPA: 8.67 / 10.0

\section{Industrial Experience}
\datedsubsection{\textbf{American Family Insurance.} Madison, WI}{May 2018 -- Present}
\role{Data Analytics Intern}{Manager: Mingju Sun}
Deploying and maintaining cloudmatcher solution to solve matching problems in the insurance domain.
\begin{itemize}
  \item Deployed cloudMatcher as a macro-service to help multiple business teams do entity matching, deduplication, etc.
  \item Identifying bottleneck and optimizing pieces of the end-to-end workflow for large datasets.
\end{itemize}

\datedsubsection{\textbf{Huawei Technologies.} Santa Clara, CA}{May 2015 -- Aug 2015}
\role{Systems Software Intern}{Manager: John Wei}
Worked on extending the IceFS solution to isolate metadata in Ext3 file system dynamically based on the size of file system.
\begin{itemize}
  \item Implemented space isolation to remove read-only problem when a particular block group corrupts
  \item Enhanced user level tools (mke2fs, dumpe2fs, e2fsck, etc.) and added admin tool for monitoring
\end{itemize}

\datedsubsection{\textbf{Syntel - Humana Inc.} GreenBay, WI}{Oct 2009 -- Aug 2014}
\role{Software Engineer/Project Lead}{}
Involved in developing and maintaining web-services and business solutions for various applications.
\begin{itemize}
  \item Developed mainframe solutions for old legacy system using CICS, COBOL, JCL, MQ series.
  \item Developed and maintained service oriented architecture by web service development (WCF), SQL performance enhancements, SSIS packages.
\end{itemize}

\datedsubsection{\textbf{Tech Mahindra (Client: CIGNA)} India}{Sep 2007 -- Oct 2009}
\role{Software Developer}{}
Worked as a mainframe developer/production support analyst.

\section{Research Experience}
\datedsubsection{\textbf{University of Wisconsin - Madison.} Madison, WI}{Feb 2016 -- Present}
\role{Research Assistant}{Advisor: AnHai Doan}
Building a cloud/crowd based Entity Matching solution: cloudmatcher
\begin{itemize}
  \item Primary research focusses on identifying techniques to develop a large scale robust cloud/crowd based system for entity matching using machine learning
and crowdsourcing operations.
  \item Design platform where users can plug/play services to perform different operations in the data integration space.
\end{itemize}

\datedsubsection{\textbf{University of Wisconsin - Madison.} Madison, WI}{Sep 2014 -- May 2015}
\role{Research Assistant}{Advisor: Remzi Arpaci-Dusseau}
Worked on understanding Copy on Write (CoW) behavior in B-tree file systems 
\begin{itemize}
  \item Implemented a prototype to understand how CoW works in LFS and B-tree file systems
  \item Identifying how data/metadata are stored on file system and their behavior on system crashes
\end{itemize}

\section{Publications}
\begin{itemize}
  \item \emph{Entity Matching Meets Data Science: A Progress Report from the Magellan Project}, {SIGMOD'19 (Industrial)} \\
Yash Govind, P.Konda, Paul S. G.C., P. Martinkus, P. Nagarajan, A. Soundararajan, H. Li, S. Mudgal, J. R. Ballard, H. Zhang, A. Ardalan, S. Das, D. Paulsen, A. Saini, E. Paulson, Y. Park, M. Carter, M. Sun, G. M. Fung, A. Doan
  \item \emph{CloudMatcher: A Hands-off Cloud/Crowd Service for Entity Matching: [Demonstration Proposal]}, {VLDB'18} \\
Yash Govind, E. Paulson, P. Nagarajan, Paul S. G.C., A. Doan, Y. Park, G. M. Fung, D. Conathan, M. Carter, M. Sun
  \item \emph{Toward a System Building Agenda for Data Integration (and Data Science)}, {IEEE DEB'18} \\
A. Doan, P. Konda, Paul S. G.C., A. Ardalan, J. R. Ballard, S. Das, Yash Govind, H. Li, P. Martinkus, S. Mudgal, E. Paulson, H. Zhang
  \item \emph{Magellan: Toward Building Entity Matching Management Systems[Sigmod Research Highlight]}, {SIGMOD Research Highlight'18} \\
P. Konda, S. Das, Paul S. G.C., P. Martinkus, A. Doan, A. Ardalan, J. R. Ballard, Yash Govind, H. Li, F. Panahi, H. Zhang, Jeff Naughton, S. Prasad, G. Krishnan, R. Deep
  \item \emph{CloudMatcher: A Cloud/Crowd Service for Entity Matching}, {BigDAS @ KDD' 17} \\
Yash Govind, E. Paulson, M. Ashok, Paul G.C., A. Hitawala, A. Doan, Y. Park, P. Peissig, E. LaRose, J. Badger
  \item \emph{Human-in-the-Loop Challenges for Entity Matching: A Midterm Report}, {HILDA @ Sigmod'17} \\
A. Doan, A. Ardalan, J.R. Ballard, S. Das, Yash Govind, P. Konda, H. Li, S. Mudgal, E. Paulson, Paul G.C., H. Zhang
\end{itemize}

\section{Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages \& Tools: Python, C++, C, HTML, Javascript, SQL, Mainframe, Git.
  \item Data Science Tools: Pandas, Scikit-learn, Networkx, Numpy, Dask, Anaconda.
\end{itemize}

\section{Coursework}
\begin{itemize}[parsep=0.5ex]
  \item Big Data and Databases: Big Data Systems, Advanced Databases, Data Models and Languages
  \item Systems: Introduction to OS, Advanced OS, Distributed Systems
  \item Others: Introduction to AI/ML, Networks, Optimization, HR strategy, Understanding data in Psychology
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{Activities}
\begin{itemize}
  \item \textbf{Chair, ACM Student Chapter, UW-Madison}, organized social and technical events for CS students
  \item \textbf{Tech volunteer: Clean Lakes Alliance, Madison}, helped building a eco-yard tool to score your yard and give recommendation
  \item \textbf{Head, Placement Coordinator Cell, SSTC}, organized mock technical and non-techincal interviews for CSE students
  \item \textbf{Member, Graduate Studies Committee, SSTC}, help students prepare for graduate school
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
